Texture mapping 3D planar models of indoor environments with noisy camera poses

### 2012-12-23 spie/paper.tex
intro parts

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{abstract}
abstract goes here and stuff
\end{abstract}

%>>>> Include a list of keywords after the abstract

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
\label{sec:intro}  % \label{} allows reference to this section

This document shows the desired format and appearance of a manuscript prepared for the Proceedings of the SPIE.\footnote{The basic format was developed in 1995 by Rick Herman (SPIE) and Ken Hanson (Los Alamos National Lab.).} It is prepared using LaTeX2e\cite{Lamport94} with the class file {\tt spie.cls}.  The LaTeX source file used to create this document is {\tt article.tex}, which contains important formatting information embedded in it.  These files are available on the Internet at {\tt http://home.lanl.gov/kmh/spie/}.  The font used throughout is the LaTeX default font, Computer Modern Roman, which is equivalent to the Times Roman font available on many systems.  If this font is not available, use a similar serif font.  Normal text has a font size of 10 points\footnote{Font sizes are specified in points, abbreviated pt., which is a unit of length.  One inch = 72.27 pt.; one cm = 28.4 pt.} for which the actual height of a capital E is about 2.4 mm (7 pt.) and the line-to-line spacing is about 4.2 mm (12 pt.).  The font attributes for other parts of the manuscript, summarized in Table~\ref{tab:fonts}, are described in the following sections.  Normal text should be justified to both the left and right margins.  Appendix~\ref{sec:latex} has information about PostScript fonts.

To be properly reproduced in the Proceedings, all text and figures must fit inside a rectangle 6.75-in.\ wide by 8.75-in.\ high or 17.15 cm by 22.23 cm.  The text width and height are set in {\tt spie.cls} to match this requirement.
%% This table is carefully placed in the source file to make 
%% it appear at bottom of page, but above the footnotes.  
%% Use of [h] in following command forces table to appear "here".
\begin{table}[h]
\caption{Fonts sizes to be used for various parts of the manuscript.  All fonts are Computer Modern Roman or an equivalent.  Table captions should be centered above the table.  When the caption is too long to fit on one line, it should be justified to the right and left margins of the body of the text.} 
\label{tab:fonts}
\begin{center}       
\begin{tabular}{|l|l|} %% this creates two columns
%% |l|l| to left justify each column entry
%% |c|c| to center each column entry
%% use of \rule[]{}{} below opens up each row
\hline
\rule[-1ex]{0pt}{3.5ex}  Article title & 16 pt., bold, centered  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Author names and affiliations & 12 pt., normal, centered   \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Section heading & 11 pt., bold, centered (all caps)  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Subsection heading & 11 pt., bold, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Sub-subsection heading & 10 pt., bold, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Normal text & 10 pt., normal  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Figure and table captions & \, 9 pt., normal \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Footnote & \, 9 pt., normal \\
\hline 
\end{tabular}
\end{center}
\end{table} 
The text should begin 1.00 in.\ or 2.54 cm from the top of the page.  The right and left margins should be 0.875~in.\ or 2.22 cm for US letter-size paper (8.5 in.\ by 11 in.) or 1.925 cm for A4 paper (210 mm by 297 mm) to horizontally center the text on the page.  See Appendix~\ref{sec:latex} for guidance regarding paper-size specification.

Authors are encouraged to follow the principles of sound technical writing, as described in Refs.~\citenum{Alred03} and \citenum{Perelman97}, for example.  Many aspects of technical writing are addressed in the {\em AIP Style Manual}, published by the American Institute of Physics.  It is available on line at {\tt http://www.aip.org/pubservs/style/4thed/toc.html} or {\tt http://public.lanl.gov/kmh/AIP\verb+_+Style\verb+_+4thed.pdf}. A spelling checker is helpful for finding misspelled words.

An author may use this LaTeX source file as a template by substituting his/her own text in each field.  This document is not meant to be a complete guide on how to use LaTeX.  For that, refer to books on LaTeX usage, such as the definitive work by Lamport\cite{Lamport94} or the very useful compendium by Mittelbach et al.\cite{Mittelbach04}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PARTS OF MANUSCRIPT}

@@

%%%%%Sometimes it is necessary to precede the double slash 
%%%%%by \verb|\protect| to get the desired result, 
%%%%%for example, in article titles.

%%-----------------------------------------------------------
\subsection{Title and Author Information} 
\label{sec:title}

@@

%%-----------------------------------------------------------
\subsection{Abstract and Keywords} 
The title and author information is immediately followed by the Abstract. The Abstract should concisely summarize the key findings of the paper.  It should consist of a single paragraph containing no more than 200 words.  The Abstract does not have a section number.  A list of up to ten keywords should immediately follow the Abstract after a blank line.  These keywords will be included in a searchable database at SPIE.

%%-----------------------------------------------------------
\subsection{Body of Paper} 
The body of the paper consists of numbered sections that present the main findings.  These sections should be organized to best present the material.  See Sec.~\ref{sec:sections} for formatting instructions.

%%-----------------------------------------------------------
\subsection{Appendices} 
Auxiliary material that is best left out of the main body of the paper, for example, derivations of equations, proofs of theorems, and details of algorithms, may be included in appendices.  Appendices are enumerated with uppercase Latin letters in alphabetic order, and appear just before the Acknowledgments and References.

%%-----------------------------------------------------------
\subsection{Acknowledgments} 
In the Acknowledgments section, appearing just before the References, the authors may credit others for their guidance or help.  Also, funding sources may be stated.  The Acknowledgments section does not have a section number.

%%-----------------------------------------------------------
\subsection{References} 
The References section lists books, articles, and reports that are cited in the paper.  It does not have a section number.  The references are numbered in the order in which they are cited.  Examples of the format to be followed are given at the end of this document.

@@

%%-----------------------------------------------------------
\subsection{Footnotes} 
Footnotes\footnote{Footnotes are indicated as superscript symbols to avoid confusion with citations.} may be used to provide auxiliary information that doesn't need to appear in the text, e.g., to explain measurement units.  They should be used sparingly, however.

@@

%%-----------------------------------------------------------
\subsection{Subsection Attributes}

@@

%%-----------
\subsubsection{Sub-subsection attributes} 
The sub-subsection heading is left justified and its font is 10 point, bold.  Capitalize as for sentences.  The first word of a sub-subsection heading is capitalized.  The rest of the heading is not capitalized, except for acronyms and proper names.

@@

Tables are handled identically to figures, except that their captions appear above the table. 
%%  Use following command to specify that graphics file is in 
%%  a directory other than this LaTeX source file.
%%  Note use of / to separate subdirectories, for UNIX and Windows OS.
%%\graphicspath{{H:/HANSON/SPIESTY/}}
%% tabular environment useful for creating an array of images  
%-------------
   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=7cm]{naive.jpg}
   \end{tabular}
   \end{center}
   \caption[example] 
%>>>> use \label inside caption to get Fig. number with \ref{}
   { \label{fig:example} 
Figure captions are used to describe the figure and help the reader understand it's significance.  The caption should be centered underneath the figure and set in 9-point font.  It is preferable for figures and tables to be placed at the top or bottom of the page. LaTeX tends to adhere to this standard.}
   \end{figure} 
%-------------

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{abstract}
  Automated 3D modeling of building interiors is used in applications
  such as virtual reality and environment mapping. Incorporating
  images and texture mapping these models allows for photorealistic
  visualizations of the data collected by such modeling systems. Pose
  estimates obtained by these systems often suffer from inaccuracies,
  resulting in visible discontinuities when successive images are
  projected adjacently onto a surface for texturing. Existing methods
  to stitch images together are often computationally expensive and
  work independently of pose estimates and geometry information. We
  propose a method to refine camera poses using both existing
  estimates and geometry information, followed by two different
  methods to composite images together, based on the uniformity of
  available images. The effectiveness of our methods are demonstrated
  on a number of disparate indoor environments.
\end{abstract}

% >>>> Include a list of keywords after the abstract

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
\label{sec:introduction} % \label{} allows reference to this section
Three-dimensional modeling of indoor environments has a variety of
applications such as training and simulation for disaster management,
virtual heritage conservation, and mapping of hazardous sites. Manual
construction of these digital models can be time-consuming, and as a
result, automated 3D site modeling has garnered much interest in
recent years. CITATION

The first step in automated 3D modeling is the physical scanning of
the environment's geometry. An indoor modeling system must recover its
own poses within an environment while simultaneously reconstructing
the 3D structure of the environment itself. CITATION. This is known as
the simultaneous localization and mapping (SLAM) problem, and is
generally solved by taking readings from laser range scanners,
cameras, and inertial measurement units (IMUs) at multiple locations
within the environment.

In this paper, we work with data obtained from a backpack-mounted
system, carried by an ambulatory human. Such a system provides
advantages over more common wheel-mounted systems in terms of agility
and portability, but results in much higher localization error and
uncertainty overall. CITATION. As a result, common methods for texture
mapping generally produce poor results, leading to the development of
the approaches contained in this paper. Besides localization
information and images, environment geometry is required as well for
texture mapping. In this paper we work mainly with models obtained
through plane-fitting surfaces to point clouds generated by the
backpack system. CITATION. We have also developed an appropriate
method to work with near-planar models, as described in APPENDIX
SOMETHING.

Though our texture mapping procedure was designed with the
aforementioned system in mind, it is easily generalizable to any other
system, provided the required inputs of surface geometry, images with
rough extrinsic pose estimates, and either provided or estimated
intrinsic camera calibration matrices. An added benefit of our method
is its relatively fast running time and modularity of each step,
allowing for quick tuning of parameters and easy accomodation of new
input data given updates in localization or model-generation
algorithms.

The remainder of the paper is organized as follows. Section X explains
how input images are projected onto our geometry and simple approaches
towards texturing. Section X covers more sophisticated existing
approaches to image matching and stitching, and their performance on
our datasets. Section X contains our approach towards image matching,
followed by Section X, which describes compositing approaches. Section
X contains further results and conclusions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PARTS OF MANUSCRIPT}

@@

%%%%% Sometimes it is necessary to precede the double slash by
%%%%% \verb|\protect| to get the desired result, for example, in
%%%%% article titles.

%% -----------------------------------------------------------
\subsection{Title and Author Information}
\label{sec:title}

@@

%% -----------------------------------------------------------
\subsection{Abstract and Keywords}
The title and author information is immediately followed by the
Abstract. The Abstract should concisely summarize the key findings of
the paper.  It should consist of a single paragraph containing no more
than 200 words.  The Abstract does not have a section number.  A list
of up to ten keywords should immediately follow the Abstract after a
blank line.  These keywords will be included in a searchable database
at SPIE.

%% -----------------------------------------------------------
\subsection{Body of Paper}
The body of the paper consists of numbered sections that present the
main findings.  These sections should be organized to best present the
material.  See Sec.~\ref{sec:sections} for formatting instructions.

%% -----------------------------------------------------------
\subsection{Appendices}
Auxiliary material that is best left out of the main body of the
paper, for example, derivations of equations, proofs of theorems, and
details of algorithms, may be included in appendices.  Appendices are
enumerated with uppercase Latin letters in alphabetic order, and
appear just before the Acknowledgments and References.

%% -----------------------------------------------------------
\subsection{Acknowledgments}
In the Acknowledgments section, appearing just before the References,
the authors may credit others for their guidance or help.  Also,
funding sources may be stated.  The Acknowledgments section does not
have a section number.

%% -----------------------------------------------------------
\subsection{References}
The References section lists books, articles, and reports that are
cited in the paper.  It does not have a section number.  The
references are numbered in the order in which they are cited.
Examples of the format to be followed are given at the end of this
document.

@@

%% -----------------------------------------------------------
\subsection{Footnotes}
Footnotes\footnote{Footnotes are indicated as superscript symbols to
  avoid confusion with citations.} may be used to provide auxiliary
information that doesn't need to appear in the text, e.g., to explain
measurement units.  They should be used sparingly, however.

@@

%% -----------------------------------------------------------
\subsection{Subsection Attributes}

@@

%% -----------
\subsubsection{Sub-subsection attributes}
The sub-subsection heading is left justified and its font is 10 point,
bold.  Capitalize as for sentences.  The first word of a
sub-subsection heading is capitalized.  The rest of the heading is not
capitalized, except for acronyms and proper names.

@@

Tables are handled identically to figures, except that their captions
appear above the table.
%% Use following command to specify that graphics file is in a
%% directory other than this LaTeX source file.  Note use of / to
%% separate subdirectories, for UNIX and Windows OS.
%% \graphicspath{{H:/HANSON/SPIESTY/}} tabular environment useful for
%% creating an array of images
% -------------
\begin{figure}
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[height=7cm]{naive.jpg}
    \end{tabular}
  \end{center}
  \caption[example]
  % >>>> use \label inside caption to get Fig. number with \ref{}
  { \label{fig:example} Figure captions are used to describe the
    figure and help the reader understand it's significance.  The
    caption should be centered underneath the figure and set in
    9-point font.  It is preferable for figures and tables to be
    placed at the top or bottom of the page. LaTeX tends to adhere to
    this standard.}
\end{figure}
% -------------
